---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ColorNameR

<!-- badges: start -->
<!-- badges: end -->

While coordinates in a space such as RGB or CIELab are useful to represent
colors, a descriptive name is sometimes more appropriate to distinguish them
in a qualitative way. For instance, it is commonplace to discriminate the colors 
of plants, flowers, and fruits using color charts provided by institutions like
the Royal Horticultural Society (RHS), which provide a finite number of categories
to where colors can be fit. Although these categories do not have a meaningful
name, the Union for the Protection of New Varieties of Plants (UPOV) presents
a glossary where each of them are translated to a more natural name.

ColorNameR is a small library that provides a `name()` function

## Installation

You can install the development version of ColorNameR from [GitHub](https://github.com/) with:

```r
# install.packages("devtools")
devtools::install_github("msanchez-beeckman/ColorNameR")
```

## Example

```{r example}
library(ColorNameR)
library(tibble)
library(ggplot2)
library(RColorBrewer)

# palette_colors <- grDevices::palette.colors(15, palette="R4")
palette_colors <- brewer.pal(12, "Paired")
names(palette_colors) <- palette_colors

tibble(color=palette_colors, value=1L) %>%
  dplyr::mutate(name=name(t(col2rgb(.data[["color"]])) / 255, colorspace="sRGB")) %>%
  ggplot(aes(x=color, y=value)) +
    geom_col(aes(fill=color)) +
    geom_label(aes(label=name), position=position_stack(vjust = 0.5)) +
    scale_fill_manual(values=palette_colors) +
    scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
    coord_flip() +
    theme(legend.position="none",
          axis.title=element_blank(), axis.ticks=element_blank(),
          axis.text.x=element_blank(), panel.background=element_blank())
```
